### 2015-05-26 writing/SNLI paper/corpus.tex
Merge remote-tracking branch 'origin/master'
Conflicts:
	writing/SNLI paper/corpus.tex
Corpus tweaks.
Nix label freq table.

% I suggest removing this sentence. It sounds like a negative, but
% there is no practical alternative except what we did do.
%
% The majority of the sentence pairs in the corpus have not been reviewed by anyone since their construction as part of the data collection Mechanical Turk task, except to remove a small number of cases where either a response field was empty or the original author flagged the source caption for review.
In order to measure the quality of our corpus, and in order to construct maximally useful testing and development sets, we performed an additional round of validation for about 10\% of our data.
This validation phase was not fundamentally different from the Mechanical Turk labeling task used to label the SICK entailment data: we presented workers with pairs of sentences (in our case, in batches of five), and ask them to choose a single label for each pair. We supplied each pair to four annonators, yielding five labels per pair including the label used by the original author. The instructions were broadly similar to the instructions for initial data collection shown in Fig.~\ref{instructions-1}, and linked to a similar FAQ. Though we used a very restrictive qualification (based on past approval rate) to select workers, we nonetheless discovered and deleted some instances of random guessing during an early round of validation, and subsequently instituted a fully closed qualification restricted to about 30 trusted workers.
\todo{Leave in mention of qual? I would--CP}

For each pair that we validated, we chose a gold label. If any one of
the three labels was chosen by at least three of the five annotators,
that label is the gold label. If there was no such consensus, which
occurred in about 0.2\% of cases, we chose the label `-'. While these
unlabeled examples are included in the corpus distribution, they are
unlikely to be helpful for the standard NLI classification task, and
we do not include them when training and evaluating the models
discussed in later sections. The results of this validation process
are summarized in Tables \ref{validation-stats} and
\ref{validation-freq}. Nearly all of the examples received a majority
label, indicating broad consensus about the nature of the data and
categories. The gold-labeled examples are essentially evenly
distributed across the three categories in our train, development, and
testing (Table~\ref{validation-freq}). The Fleiss $\kappa$ scores in
Table~\ref{kappas} are likely to be conservative given our large and
unevenly distributed pool of workers, but they still provide insights
about the levels of disagreement across the three semantic
classes. This disagreement likely reflects not just the limitations of
large crowdsourcing efforts but also the uncertainty inherent in NLI.
Regardless, the overall rates of agreement is extremely high,
suggesting that the corpus is sufficiently high quality to pose a
challenging but realistic machine learning task.

@@

Table~\ref{snli-examples} shows a set of randomly chosen validated examples from the development set with their labels. Qualitatively, we find the data that we collected to draw fairly extensively on commonsense knowledge, suggesting that superficial word alignment models are unlikely to be able to succeed at classification. We find the sentences that we collected be largely fluent, correctly spelled English, with a mix of full sentences and caption-style noun phrase fragments. Punctuation and capitalization are only intermittently present.

% Does this mean that expected punctuation is missing, or that the
% sentences required little punctuation even by prescriptive
% standards?

@@

\begin{figure}
\center
\includegraphics[width=3.05in]{length_dist}
    % From 1.0rc2
\todo{Replace w/ mean+SD if low on space.}
\caption{\label{b-table}The distribution of sentence length.} 
\end{figure}

@@

%%%%% This is the first table I would cut to save space.
%%%%% I summarized its content quickly in the prose. CP
%
\begin{table}
\center
  %\setlength{\tabcolsep}{15pt}
  %\renewcommand{\arraystretch}{1.2}
  \begin{tabular}{l lll} 
    \toprule
\textbf{Label} & \textbf{Train} & \textbf{Dev} & \textbf{Test}\\
\midrule
\ii{entailment} &		33.3 & 	33.3 & 	33.7 \\
\ii{neutral} & 		33.2 & 	32.4 & 	32.2 \\
\ii{contradiction} &  	33.3 & 	32.7 & 	32.4  \\
- (no consensus) & 	0.1 & 	1.6 & 	1.8 \\
\bottomrule
  \end{tabular}	
% From 1.0rc3
\caption{\label{validation-freq}Frequency (\%) of each label in the corpus. Note that examples without gold labels are omitted in standard evaluations.} 
\end{table}

>>>>

In order to measure the quality of our corpus, and in order to construct maximally useful testing and development sets, we performed an additional round of validation for about 10\% of our data.
This validation phase was not fundamentally different from the Mechanical Turk labeling task used to label the SICK entailment data: we presented workers with pairs of sentences (in our case, in batches of five), and ask them to choose a single label for each pair. We supplied each pair to four annonators, yielding five labels per pair including the label used by the original author. The instructions were broadly similar to the instructions for initial data collection shown in Fig.~\ref{instructions-1}, and linked to a similar FAQ. Though we used a very restrictive qualification (based on past approval rate) to select workers, we nonetheless discovered and deleted some instances of random guessing during an early round of validation, and subsequently instituted a fully closed qualification restricted to about 30 trusted workers.
%\todo{Leave in mention of qual? I would--CP Settled -SB}

For each pair that we validated, we chose a gold label. If any one of
the three labels was chosen by at least three of the five annotators,
that label is the gold label. If there was no such consensus, which
occurred in about 0.2\% of cases, we chose the label `-'. While these
unlabeled examples are included in the corpus distribution, they are
unlikely to be helpful for the standard NLI classification task, and
we do not include them when training and evaluating the models
discussed in later sections. The results of this validation process
are summarized in Table \ref{validation-stats}. 
Nearly all of the examples received a majority
label, indicating broad consensus about the nature of the data and
categories. The gold-labeled examples are essentially evenly
distributed across the three categories in our train, development, and
testing. The Fleiss $\kappa$ scores in
Table~\ref{kappas} are likely to be conservative given our large and
unevenly distributed pool of workers, but they still provide insights
about the levels of disagreement across the three semantic
classes. This disagreement likely reflects not just the limitations of
large crowdsourcing efforts but also the uncertainty inherent in NLI.
Regardless, the overall rates of agreement is extremely high,
suggesting that the corpus is sufficiently high quality to pose a
challenging but realistic machine learning task.

@@

Table~\ref{snli-examples} shows a set of randomly chosen validated examples from the development set with their labels. Qualitatively, we find the data that we collected to draw fairly extensively on commonsense knowledge, suggesting that superficial word alignment models are unlikely to be able to succeed at classification. We find the sentences that we collected be largely fluent, correctly spelled English, with a mix of full sentences and caption-style noun phrase fragments. Punctuation and capitalization are often omitted.

@@

\begin{figure}
\center
\includegraphics[width=3.05in]{length_dist}
    % From 1.0rc2, though still accurate as of rc3
\todo{Replace w/ mean+SD if low on space.}
\caption{\label{b-table}The distribution of sentence length.} 
\end{figure}

@@
